% LaTeX2e Template by Stephen Iota (https://stepheniota.com/)
% last updated: Jan. 2019

% for papers
%\documentclass[aps,onecolumn,superscriptaddress]{revtex4-1}
% https://www-d0.fnal.gov/Run2Physics/WWW/templates/revtex4.pdf
% https://cdn.journals.aps.org/files/revtex/auguide4-1.pdf
% for revTeX4-1 class options

% for other
\documentclass[10pt]{article}
\usepackage[margin=2cm]
{geometry}

%%%%%%%%%%%%%%%%
%%% Packages %%%
%%%%%%%%%%%%%%%%

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts} % to remove math font when typesetting equations
\usepackage[thinc]{esdiff} 
\usepackage{graphicx}
\usepackage[shortlabels]{enumitem} % to change labels in enum/item
\usepackage[dvipsnames]{xcolor} % for colored links

% always put this at the end
\usepackage[
	colorlinks=true,
	citecolor=green!50!black,
	linkcolor=NavyBlue!75!black,
	urlcolor=green!50!black,
	hypertexnames=false]{hyperref} 

 
 %%%%%%%%%%%%%%%%%%
 %% New Commands %%
 %%%%%%%%%%%%%%%%%%
 
\newcommand{\email}[1]{\texttt{\href{mailto:#1}{#1}}}

\newcommand{\hint}[1]{\color{Blue}{#1}}
 
%----------------------------------------------------
%%%%%%%%%%%%%%%%%%
%% Front Matter %%
%%%%%%%%%%%%%%%%%%

\pagenumbering{gobble} % no page numbers
\graphicspath{{figures/}} % set directory for figures
%\usepackage{wrapfig}
\setcounter{section}{-1} % start with section 0

%%%%%%%%%%%%%
%%% Title %%%
%%%%%%%%%%%%%
\begin{document}

\begin{center}

\Large{\textsc{Week 4}: \textbf{Kinematics in 2D}}

\end{center}

\vspace{.5mm}


%%%%%%%%%%
%% INFO %%
%%%%%%%%%%

\begin{tabular}{rl}
\textsc{SI Leader}:
&
Stephen Iota (\email{siota001@ucr.edu})
\\
\textsc{Course}:
&
Physics 40A (Winter 2019), Prof.~Ellison
\\
\textsc{Date}:
&
28 January 2019
\end{tabular}

%%%%%%%%%%%%%%
%% PROBLEMS %%
%%%%%%%%%%%%%%


\section{Getting Comfortable with Vectors}
\begin{equation*}
	\mathbf{A} = 9 \hat{x} + 18 \hat{y} + 27 \hat{z}
\end{equation*}
\begin{equation*}
	\mathbf{B} = 3 \hat{x} - 4 \hat{y} + 5 \hat{z}
\end{equation*}
\begin{equation*}
	\mathbf{C} =  10 \hat{y} + 4 \hat{z}
\end{equation*}

\begin{enumerate}[(a)]
	\item Can I add a vector and a scalar together?
	\item Compute $\mathbf{D} = \mathbf{A} - \mathbf{B} + \frac{1}{2}\mathbf{C}$.
	\item Find the magnitudes of the vectors $\mathbf{A}, \mathbf{B}, \ \mathrm{and} \ \mathbf{C}.$
	\item Write $\mathbf{C}$ as a linear combination of $\mathbf{A} \ \mathrm{and} \ \mathbf{B}$, i.e. $ \mathbf{C} = \alpha\mathbf{A} + \beta\mathbf{B}.$

\end{enumerate}

\section{Lost at Sea}
A captain and his ship leave harbor A at $v_0= 20$ m/s, traveling due north towards harbor B, which is 72 km away. 30 min into the voyage, a strong wind in the E direction blows at $v_{\mathrm{wind}} = 5$ m/s. The captain and his crew did not adjust their course to correct for the wind, end up getting lost at sea, and do not reach their destination. 
\\
\textsc{Note:} Assume the shores are infinite straight lines in the EW direction, and ignore water resistance and drag.

\begin{enumerate}[(a)]
	\item How long would it have taken the ship to cross from harbor A to B if there was no wind?	
	\item How long does their journey end up taking? Assume harbor B lies along a straight, infinite coast in the EW direction.
	\item How far east from harbor B does the ship end up? 
	\item At what angle should have the captain and his have steered in when the wind started to arrive at harbor B? 
\end{enumerate}


\section{Circular Motion}
\begin{enumerate}[(a)]

\item When working with uniform circular motion, we can describe motion in 2D with 1 independent variable. How do we do this?
\item What is the relation between tangential velocity $v_\mathrm{t}$ and angular velocity $\omega$?
\item How do we express angular acceleration in terms of velocity? What about $\omega$?	

\end{enumerate}


\section{Cyclotron Frequency}

Electrons in a constant, transverse Magnetic field undergo centripetal acceleration. If an electron has a period of oscillation $T = 2 \ \mathrm{ms}$ and a radius of orbit of $r = 6 \ \mu\mathrm{m}.$ Find:
\begin{enumerate}[(a)]
	\item the electron's frequency\footnote{\url{https://en.wikipedia.org/wiki/Electron_cyclotron_resonance}} $\omega$ of oscillation
	\item the electron's speed $v$
	\item and the magnitude of it's acceleration $a$.
\end{enumerate}


\noindent
Notice that the electron's speed is a constant! If you think this is interesting, look into (a) Work and (b) conservative v non-conservative vector fields on Wiki.


\end{document}